An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}

### 2018-02-10 paper/ms.tex
stars are pretty

The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{*}}$ can be
expressed as
\begin{align}
    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
\end{align}

@@

Then, the CBV-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
\end{equation}

@@

% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
% Do you use AIC or BIC or cross-validation?
An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
as follows
\begin{align}
    n^{*} = \argmin_{n} \dfrac{p_{n+1}}{p_n},
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.

@@

Briefly, the PSF photometry problem that lightkurve solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector
$\bm{\theta}^{*} = (\theta_1^{*}, \theta_2^{*}, ..., \theta_m^{*})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{*}$.

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption on the data is that it follows
a Poisson probability distribution, whereas the probability distribution on the
parameter vector has to be assigned by the user using the $\texttt{prior}$
argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
as
\begin{align}
    \bm{\theta}^{*}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
    \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),
\end{align}
in which $\Lambda$ is the support of $\bm{\theta}$.

>>>>

The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{\star}}$ can be
expressed as
\begin{align}
    \bm{\theta}^{\star} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
\end{align}

@@

Then, the CBV-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{\star}_j v_{j}(t).
\end{equation}

@@

% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
% Do you use AIC or BIC or cross-validation?
An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{\star}$ number of CBVs
as follows
\begin{align}
    n^{\star} = \argmin_{n} \dfrac{p_{n+1}}{p_n},
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.

@@

Briefly, the PSF photometry problem that lightkurve solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector
$\bm{\theta}^{\star} = (\theta_1^{\star}, \theta_2^{\star}, ..., \theta_m^{\star})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{\star}$.

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption on the data is that it follows
a Poisson probability distribution, whereas the probability distribution on the
parameter vector has to be assigned by the user using the $\texttt{prior}$
argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
as
\begin{align}
    \bm{\theta}^{\star}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
    \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),
\end{align}
in which $\Lambda$ is the support of $\bm{\theta}$.
